---
title: "BOZ 780 - Pre-assignment 1"
output: html_notebook
author: "Damien Sousa de Gouveia 150003079"
---
```{r, echo=FALSE, results='hide', warning=FALSE}
library(tidyverse)
library(lpSolve)

insto_matrix <- function(len, index){
  out <- rep(0,len)
  out[index] <- 1
  return(out)
}
library(gMOIP)

```


# 1 Rardin, Problem 2-22
### Problem formulation

The following decision variables and parameters are defined.
$$
\begin{align}
s_i &= \text{\{1 = site selected, 0 = site not selected \}} \\
c_i &= \text{cost per site} \\
a_{ji} &= \text{availbility per site $i$ per region $j$ } \\
&i \in \{1,\dots,4\} \\
&j \in \{1,\dots,5\}
\end{align}
$$

The following objective function is formulated to calculate the site cost

$$
\begin{align}
\min z = \sum_{i=1}^4 s_i \times c_i
\end{align}
$$

Subject to the following constraints

$$
\begin{align}
\sum_{i=1}^4 s_i \times a_{ji} &>= 1 &\forall j \in \{1,\dots,5\} \\
\sum_{i=1}^4 s_i &<= 4 &i \in \{1,\dots,4\} \\
\end{align}
$$

### Solution
The decision variables and parameters are initiated
```{r}
i <- 4
j <- 5
c_i <- c(200,40,55,75) 
```
The constraints are formulated algebraically
```{r}
cons_1 <- rep(1,i)
cons_j1 <- matrix(insto_matrix(len = i, c(1,2)),nrow = 1, ncol = i) # well 1 supply limit
cons_j2 <- matrix(insto_matrix(len = i, c(1,2,3)),nrow = 1, ncol = i) # well 1 supply limit
cons_j3 <- matrix(insto_matrix(len = i, c(1,3,4)),nrow = 1, ncol = i) # well 1 supply limit
cons_j4 <- matrix(insto_matrix(len = i, c(1,2)),nrow = 1, ncol = i) # well 1 supply limit
cons_j5 <- matrix(insto_matrix(len = i, c(1,4)),nrow = 1, ncol = i) # well 1 supply limit
```

The solution is calculated using the $lpSolve$ interface
```{r}
# Set coefficients of the objective function
f.obj <- c_i

# Set matrix corresponding to coefficients of constraints by rows
# Do not consider the non-negative constraint; it is automatically assumed
f.con <- rbind(cons_1, cons_j1, cons_j2, cons_j3, cons_j4, cons_j5)
f.con

# Set inequality signs
f.dir <- c("<", #cons_1
           rep(">=",j)) #cons_j1 - consj5


# Set right hand side coefficients
f.rhs <- c(4, #cons_1
           rep(1,j)) #cons_j1 - consj5

# Final value (z)
lp("min", f.obj, f.con, f.dir, f.rhs, all.bin = TRUE)

# Variables final values
lp("min", f.obj, f.con, f.dir, f.rhs, all.bin = TRUE)$solution

```



# 2 Rardin, Problem 2-27
### Problem formulation
The following decision variables and parameters are defined.
$$
\begin{align}
x_i &= \text{pumping rate for the $i$'th pump in gal/min} \\ 
c_i &= \text{cost for operating the $i$'th pump in \$/gal/min} \\
l_i &= \text{upper pumping limit the $i$'th pump in gal/min} \\
w_j &= \text{upper supply limit for well the $j$'ith well in gal/min} \\
d &= \text{city demand in gal/min} \\
&i \in \{1,\dots,10\} \\
&j \in \{1,2,3\}
\end{align}
$$

The following objective function is defined to quantify the pumping cost.

$$
\begin{align}
\min(z) =\sum_{i=1}^{10}x_i\times c_i
\end{align}
$$

Subject to the following constraints 

$$
\begin{align}
x_i &<= l_i & \forall i \in \{1,\dots,10\} \\ 
x_1 + x_4 + x_7 &<= w_1 \\
x_2 + x_5 + x_8 &<= w_2 \\
x_3 + x_6 + x_9 +x_{10} &<= w_3 \\
\sum_{i=1}^{10}x_i &>= d &i \in \{1,\dots,10\}\\
\end{align}
$$

### Solution
The decision variables and parameters are initiated
```{r}
i <- 10
j <- 3
x_i <- rep(0,i)
c_i <- c(0.05,0.05,0.05,0.07,0.07,0.07,0.13,0.13,0.13,0.13) 
l_i <- c(1100,1100,1100,1500,1500,1500,2500,2500,2500,2500)
w_j <- c(3000,2500,7000)
d <- 10000
```
The constraints are formulated algebraically
```{r}
cons_1 <- diag(i) #pumping limit cons
cons_2 <- matrix(insto_matrix(len = i, c(1,4,7)),nrow = 1, ncol = i) # well 1 supply limit
cons_3 <- matrix(insto_matrix(len = i, c(2,5,8)),nrow = 1, ncol = i) # well 2 supply limit
cons_4 <- matrix(insto_matrix(len = i, c(3,6,9,10)),nrow = 1, ncol = i) # well 3 supply limit
cons_5 <- matrix(rep(1,i),nrow = 1) # demand requirement
```

The solution is calculated using the $lpSolve$ interface
```{r}
# Set coefficients of the objective function
f.obj <- c_i

# Set matrix corresponding to coefficients of constraints by rows
# Do not consider the non-negative constraint; it is automatically assumed
f.con <- rbind(cons_1, cons_2, cons_3, cons_4, cons_5)

# Set inequality signs
f.dir <- c(rep("<=",i), #cons_1
           "<=", #cons_2
           "<=", #cons_3
           "<=", #cons_4
           ">=") #cons_5

# Set right hand side coefficients
f.rhs <- c(l_i, #cons_1
           w_j, #cons_2 to cons_4
           d) #cons_5

# Final value (z)
lp("min", f.obj, f.con, f.dir, f.rhs)

# Variables final values
lp("min", f.obj, f.con, f.dir, f.rhs)$solution

```

# 3 Rardin, Problem 2-28
### Problem formulation
1. The decision to select or exclude a project is binary (yes or no). If a project is taken there are fixed costs associated with it that do not scale based on the decision variable. Thus a binary decision variable aptly reifies the model. The set for which the decision variable is defined corresponds to the number of projects and this a binary decision is made for each project.

2.Symbolic names for constants
$$
\begin{align}
a_j &= \text{\{1 if resource is available 0 if resource not required \}} & j \in \{ 1, \dots , 10 \} \\
p_i &= \text{profit generated for the $i$'th project} \\
r_i &= \text{resource requirement for the $i$'th project}\\
c_i &= \text{CPU requirement for the $i$'th project}\\
\end{align}
$$
3. Objective function
$$
\begin{align}
\max z = \sum_{i=1}^8 x_i \times p_i
\end{align}
$$
4. Resource constraint
The decision variables are to be extended to include an additional set of sudo-decision variables. The decision to continue employment or retrench workers is seen as a binary decision and thus $a_j$ is included in the constraint formulation. Note that these decision variables do not form part of the cost function.
$$
\begin{align}
1. \sum_{i=1}^{8}x_i \times r_i-\sum_{j=1}^{10}a_j \times 240 \leq 0 \\
2.1\sum_{j=1}^{10}a_j  \leq 10 \\
2.2\sum_{j=1}^{10}a_j  \geq 7 \\
\end{align}
$$
4. Remaining constraints
Enforce the limit on computer time (4), meet the requirements to select at least three projects (5), and include at least one of the director’s favorites (6).
$$
\begin{align}
4.& \sum_{i=1}^{8}x_i \times c_i \leq 1 \,000 \\
5.&\sum_{i=1}^{8}x_i \geq 3\\
6.& \, x_3 + x_4 + x_5 + x_8 \geq 1 \\
\end{align}
$$

4. Variable constraints
$$
\begin{align}
x_i &\geq 0 & \forall i \in \{1,\dots,8\}\\
a_j &\geq 0 & \forall j \in \{1,\dots,10\}
\end{align}
$$

5. Model classification
The objective function and constraints are linear, convex functions with binary decision variables thus making the model an Integer Linear Program (ILP). There is a single objective function, to maximize profit and thus this problem is a single objective.

### Solution

Initialize decision variables and parameters
```{r}
i <-  8
j <- 10
mat_i <- matrix(1,1,i) #dummy matrix for x coefficients
mat_j <- matrix(1,1,j) #dummy matrix for a coefficients

p_i <- c(2.1, 0.5, 3, 2, 1, 1.5, 0.6, 1.8) #profit
r_i <- c(550, 400, 300, 350, 450, 500, 350, 200) #resource requirement
c_i <- c(200, 150, 400, 450, 300, 150, 200, 600) #cpu limit

```
The constraints are formulated algebraically
```{r}
cons_1 <- cbind(mat_i*r_i,mat_j*-240)
cons_2 <- cbind(mat_i*0,mat_j)
cons_3 <- cbind(mat_i*0,mat_j)
cons_4 <- cbind(mat_i*c_i,mat_j*0)
cons_5 <- cbind(mat_i,mat_j*0)
cons_6 <- cbind(matrix(insto_matrix(i,c(3,4,5,8)),nrow = 1),mat_j*0)
```
The solution is calculated using the $lpSolve$ interface
```{r}
# Set coefficients of the objective function
f.obj <- cbind(mat_i*p_i,mat_j*0)

# Set matrix corresponding to coefficients of constraints by rows
# Do not consider the non-negative constraint; it is automatically assumed
f.con <- rbind(cons_1, cons_2, cons_3, cons_4, cons_5, cons_6)

# Set inequality signs
f.dir <- c("<=", #cons_1
           "<=", #cons_2
           ">=", #cons_3
           "<=", #cons_4
           ">=", #cons_5
           ">=") #cons_6

# Set right hand side coefficients
f.rhs <- c(0,  #cons_1
           10,#cons_2
           7, #cons_3
           1000,#cons_4
           3,#cons_5
           1) #cons_6

# Final value (z)
lp("max", f.obj, f.con, f.dir, f.rhs, all.bin = TRUE)

# Variables final values
print("Projects")
lp("max", f.obj, f.con, f.dir, f.rhs, all.bin = TRUE)$solution[1:i]

print("Resources")
res <- lp("max", f.obj, f.con, f.dir, f.rhs, all.bin = TRUE)$solution[i+1:j]
res
paste("Resource usage at ", round(sum(res)/j*100,digits = 2),"%", sep = "")
```

# 4 Winston & Venkataramanan, Section 9.2, Problem 24
### Problem formulation
### Solution

# 5 Winston & Venkataramanan, Section 9.2, Problem 32
### Problem formulation
### Solution

# 6 Winston & Venkataramanan, Chapter 9, Review problem 24
### Problem formulation
### Solution

# 7 Trans-shipment problem
### Problem formulation
### Solution

# 8 Blending problem
### Problem formulation
### Solution